Ordnung ist das halbe Leben -- Establishing Totally Ordered HTN Planning Problems is Half the Job (to Getting them Solved More Efficiently)

### 2022-12-02 paper/03--linearization-ground.tex
some changes

Notably, the graph $G$ might \emph{not} have a topological order because it may contain cycles. That is, some ordering constraints we add might conflict with each other. If this is the case, we \emph{randomly} remove some edges $(t, t')$ from $G$ with $(t, t') \notin \parOrd{}^{+}$ (because we \emph{cannot} violate the original ordering constraints in $tn$) until there exist no cycles. We call this step \emph{cycle-breaking}. The entire procedure is shown in Alg.~\ref{alg:Algorithm1}.

>>>>

Notably, the graph $G$ might \emph{not} have a topological order because it may contain cycles. That is, some ordering constraints we add might conflict with each other. If this is the case, we \emph{randomly} remove some edges $(t, t')$ from $G$ with $(t, t') \notin \parOrd{}^{+}$ (because we must \emph{not} contradict the original ordering constraints in $tn$) until there exist no cycles. We call this step \emph{cycle-breaking}. The entire procedure for linearizing a method is summarized in Alg.~\ref{alg:Algorithm1}.

\begin{algorithm}[t]
	\input{alg-linearization.tex}
	\caption{Lineraizing a method.}
	\label{alg:Algorithm1}
\end{algorithm}

Lastly, in order to transform a partially ordered HTN planning problem into a totally ordered one, we could call Alg.~\ref{alg:Algorithm1} on every method in the input problem.
